\documentclass[14pt]{extarticle}

\input{../preamble.tex}


\begin{document}
    \title{Problems 1: Random problems}

    \begin{problems}

        \item There is a parallelogram \(ACDE\) externally constructed on the
        side \(AC\) of the triangle \(ABC\). Let \(O\) be the intersection
        point of the diagonals of \(ACDE\); \(N\) and \(K\) are midpoints of
        the sides \(BC\) and \(BA\) respectively. Prove, that lines \(DK, NE\) 
        and \(BO\) are concurrent. 

        \item In the right triangle \(ABC\) the side \(AC\) is the hypotenuse
        and \(BH\) is the altitude. Points \(D, E, F\) are chosen on the side
        \(BC\), segment \(BH\) and segment \(CH\) respectively, such that
        \(\angle BAD = \angle CAE\) and \(\angle AFE = \angle CFD\).  Prove,
        that \(\angle AEF = 90^{\circ}\).


        \item In acute triangle \(ABC\), \(BH\) is the altitude. Points \(M\)
        and \(N\) are midpoints of the segments of \(AH\) and \(CH\)
        respectively. In the circumcircle \(\Omega\) of \(BMN\), \(BB'\) is
        the diameter. Prove that \(AB' = CB'\).
        
        \item Triangle \(ABC\) is inscribed in the circle \(\omega\). Let \(M\) be
        the point on the arc \(BC\) (not containing the point \(A\)) and point
        \(M_1\) is symmetric to point \(M\) with respect to the side \(BC\).
        Prove, that segment \(AM_1\) is divided in half by the circumcircle of
        the medial triangle.

        \item Consider the triangle \(ABC\), where \(BL\) is the bisector.
        Bisector of the segment \(BL\) intersects external bisectors of angles
        \(A\) and \(C\) at points \(P\) and \(Q\) respectively. Prove, that
        the circumcircle of \(PBQ\) touches the circumcircle of \(ABC\).
    \end{problems}

\end{document}
